---
title: "HOSPITALS AND CLINICS IN BERKSHIRE COUNTY MA"
output: github_document
---

```{r setup, include=FALSE}

library(ggplot2)
library(tidyverse)
library(sf)
```

## **Hospitals and Clinics Brief Despcriptions**

* The Austen Riggs Center is a psychiatric treatment facility in Stockbridge, Massachusetts.
* Berkshire Health North provides 24-hour emergency care, a wide range of outpatient clinical and diagnostic services, outpatient surgery, and specialized health and wellness programs.
* Berkshire Health Systems is the premier provider of comprehensive health services in the Berkshires and surrounding area.
* Berkshire Medical Center is a 298-bed community teaching hospital and the recipient of numerous national recognitions for service excellence and patient safety.
* Fairview is a primary acute care hospital offering inpatient medical services, general surgery, orthopedics, and maternity services with 24-hour emergency and hospitalist coverage.
* Hillcrest Center Hillcrest Center in Lenox specializes in the treatment of adolescent girls with severe psychiatric, emotional and behavior disorders. 
* Renal Clinic, BMC Central County Dialysis Center provides state-of-the-art care for over 100 patients in the Pittsfield area. 


****
## *Data Code*

_Data Manipulation_

```{r}

# Load Data for MA boundries 
MA_counties <- USAboundaries::us_counties(resolution = "low", states = c("massachusetts")) %>%   select(-state_name) %>% 
  filter(name== "Berkshire")

# Load Data for Hospitals
hospitals_locations <- "Data/Berkshires_hospitals.csv " %>% 
  read_sf() %>% 
  st_as_sf(coords = c("lon", "lat"), crs = 4326)

```
****
### *Plot*

_Visualization of hospitals and clinics locations in Berkshire County MA._

```{r pressure, echo=FALSE}
ggplot() +
  geom_sf(data=MA_counties, aes(fill=name))+
  scale_fill_manual(values = c("#ffeda0"),name="County in Massachusetts")+
  geom_sf(data = hospitals_locations, aes(col = Hospitals))+
  labs(x="Longitude", y="Latitude", title="Hospitals and Clinics in Berkshire County")+
  theme_classic()
```


